\gettitle

### 2019-12-10 assignment4/submission4.tex
Add solution for exercise 4.2 a) and b)

\section*{2 - Transaction Processing}
\subsection*{a)}
\subsection*{b)}

>>>>

\section*{2 - Transaction Processing}
\subsection*{a)}
The conflicting operation pairs are: 
\[\{(w_1[u], w_3[u]), (r_1[y], w_2[y]), (r_3[y], w_2[y]), (r_2[x], w_3[x])\}\]

\subsection*{b)}

\begin{figure}[ht!]
\begin{tikzpicture}
    \node[draw, circle] at (0, 0)    (T1) {\(T_1\)};
    \node[draw, circle] at (5, 0)    (T2) {\(T_2\)};
    \node[draw, circle] at (2.5,2.5) (T3) {\(T_3\)};

    \draw[->]
        (T1) edge node[above,sloped] {\(w_1[y] \to r_2[y]\)} (T2)
        (T2) edge node[above,sloped] {\(w_2[z] \to w_3[z]\)} (T3)
        (T3) edge node[above,sloped] {\(w_3[y] \to r_1[y]\)} (T1);
\end{tikzpicture}
\caption{Serialization Graph for History \(H_1\)}
\label{fig:sg_h1}
\end{figure}

It's clear that the serialization graph shown in Figure \ref{fig:sg_h1} contains a cycle, as such \(H_1\) is not serializable.\\~\\

\begin{figure}[ht!]
\begin{tikzpicture}
    \node[draw, circle] at (0, 0)    (T1) {\(T_1\)};
    \node[draw, circle] at (5, 0)    (T2) {\(T_2\)};
    \node[draw, circle] at (2.5,2.5) (T3) {\(T_3\)};

    \draw[->]
        (T2) edge node[above,sloped] {\(r_2[y] \to w_1[y]\)} (T1)
        (T3) edge node[above,sloped] {\(r_3[x] \to w_1[x]\)} (T1)
        (T3) edge node[above,sloped] {\parbox[c]{2.5cm}{\(r_3[x] \to w_2[x] \\ w_3[u] \to w_2[u]\)}} (T2);
\end{tikzpicture}
\caption{Serialization Graph for History \(H_2\)}
\label{fig:sg_h2}
\end{figure}

The serialization graph shown in Figure \ref{fig:sg_h2} does not contain a cycle, which would imply that \(H_2\) is serializable.\\
Unfortunately \(H_2\) is not a correct history as it does not specify the order or the conflicting operations \(w_1[x], w_2[x]\).
